Think deep for reef resilience

### 2025-08-10 paper/paper_draft.qmd
Placeholder for citation to Canonical Reefs

Future projections of maximum yearly Degree Heating Weeks (DHWs) for each reef were
estimated from Sea Surface Temperature (SST) data for the GBR. Statistically downscaled
1km^2^ resolution SST data for five Global Climate Models (GCMs) were obtained from the
HighResCoralStress database [@dixon2022; @dixon2023]. These five GCMs were EC-Earth3-Veg,
ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GFDL-CM4 and are a part of the Sixth Phase of the
Coupled Model Intercomparison Project (CMIP6) based on evaluation conducted by Grose et al.
[-@grose2023]. These GCMs were found to rank highly in the recreation of historical
atmospheric temperature and precipitation conditions in the Australasian region. While this
assessment does not consider oceanic data, Grose et al. [-@grose2023] provide a
region-specific selection mechanism which we use as an indicator of general performance of
GCMs for the region. An overview of the selected GCMs are provided in @tbl-gcms. The process
described herein was conducted for all 2429 reefs to create DHW projections spanning from
2025 to 2075.

>>>>

Future projections of maximum yearly Degree Heating Weeks (DHWs) for each reef were
estimated from Sea Surface Temperature (SST) data for the GBR. Statistically downscaled
1km^2^ resolution SST data for five Global Climate Models (GCMs) were obtained from the
HighResCoralStress database [@dixon2022; @dixon2023]. These five GCMs were EC-Earth3-Veg,
ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GFDL-CM4 and are a part of the Sixth Phase of the
Coupled Model Intercomparison Project (CMIP6) based on evaluation conducted by Grose et al.
[-@grose2023]. These GCMs were found to rank highly in the recreation of historical
atmospheric temperature and precipitation conditions in the Australasian region. While this
assessment does not consider oceanic data, Grose et al. [-@grose2023] provide a
region-specific selection mechanism which we use as an indicator of general performance of
GCMs for the region. An overview of the selected GCMs are provided in @tbl-gcms. The process
described here was conducted for all 2429 reefs to create DHW projections spanning from 2025
to 2075. Code used to calculate DHW data and perform analyses involved in this investigation
can be found at **insert repo citation**.
